---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# M5comp
M5 Competition Data

## Installation

You can install the package `M5comp` with:

```{r gh-installation, eval = FALSE}
devtools::install_github("xqnwang/M5comp")
```

## Aggregation 

**Number of M5 series per aggregation level.**

| Level id |                        Aggregation level                             | Number of series |
|:--------:|:---------------------------------------------------------------------|-----------------:|
|   **1**  | Unit sales of all products, aggregated for all stores/states         |                1 |
|   **2**  | Unit sales of all products, aggregated for each State                |                3 |
|   **3**  | Unit sales of all products, aggregated for each store                |               10 |
|   **4**  | Unit sales of all products, aggregated for each category             |                3 |
|   **5**  | Unit sales of all products, aggregated for each department           |                7 |
|   **6**  | Unit sales of all products, aggregated for each State and category   |                9 |
|   **7**  | Unit sales of all products, aggregated for each State and department |               21 |
|   **8**  | Unit sales of all products, aggregated for each store and category   |               30 |
|   **9**  | Unit sales of all products, aggregated for each store and department |               70 |
|  **10**  | Unit sales of product x, aggregated for all stores/states            |             3049 |
|  **11**  | Unit sales of product x, aggregated for each State                   |             9147 |
|  **12**  | Unit sales of product x, aggregated for each store                   |            30490 |
| **Total**| -                                                                    |            42840 |


The following table shows more simply and clearly how the aggregated time series are generated. For example, series of level 11 are aggregated by series with the same `item.id` **and** `state.id`.

| Level id | id | item.id | dept.id | cat.id | store.id | state.id |
|:--------:|:--------:|:--------:|:--------:|:--------:|:--------:|:--------:|
|(example) | (HOBBIES_1_001_CA_1) | (HOBBIES_1_001) | (HOBBIES_1) | (HOBBIES) | (CA_1) | (CA) |
|**1**| | | | | | |
|**2**| | | | | |$\checkmark$|
|**3**| | | | |$\checkmark$| | 
|**4**| | | |$\checkmark$| | | 
|**5**| | |$\checkmark$| | | | 
|**6**| | | |$\checkmark$| |$\checkmark$| 
|**7**| | |$\checkmark$ | | |$\checkmark$ | 
|**8**| | | |$\checkmark$ |$\checkmark$ | | 
|**9**| | |$\checkmark$| |$\checkmark$| | 
|**10**| |$\checkmark$| | | | | 
|**11**| |$\checkmark$| | | |$\checkmark$| 
|**12**|$\checkmark$ | | | | | | 

## Example

The package `M5comp` contains two datasets: `M5` and `calendar`.

### M5

The `M5` is a list of $42840$ series, including $30490$ bottom-level time series and $12350$ aggregated time series. Each element of this list is also a list with some components, like the time series of the training periods and the level id of the series. The components of the bottom-level series and the aggregated series are partially different.

```{r}
# extract bottom-level series (level 12)
library(M5comp)
data(M5)
M5_bottom <- Filter(function(l) l$level == 12, M5)
# the components of the bottom-level series
names(M5_bottom[[1]])

# extract extract level 9 series
M5_l9 <- Filter(function(l) l$level == 9, M5)
# the components of the aggregated series
names(M5_l9[[1]])
# which levels the series is aggregated on
M5_l9[[1]]$agg.by
```

### calendar

The calendar data contains information about the dates the products are sold. The `calendar` object is a dataframe with some components, such as date, weekday and event_name_1.

```{r}
# the structure of the calendar data
data(calendar)
str(calendar)
```


```{r, fig.width=6, fig.height=3.5}
# plot one of the series with date
library(ggplot2)
library(xts)
library(magrittr)
ts <- M5[[1]]
xts(ts$x, order.by = calendar$date[1:ts$n]) %>% 
   autoplot() + ggtitle("Time series plot") + xlab("Time")
```


```{r}
# help pages
?M5
?calendar
```


## License

This package is free and open source software, licensed under GPL-3
